---
title: "roadrage"
author: "Olivier Haley"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Deliverables:

- Mental Health
    - Seek out high quality data across the country and apply ML to determine figures for other provinces
    
- Road Rage:
  - Seek out high quality data across the country and apply ML to determine figures for other provinces
- Using ML workflow to create connections between Mental Health and Road Rage
- "Outcome": Visual showing predictions for the two topics alongside one another
- Potential Sources: CIHI, Stats can, CMHA
- NCDB

```{r}
x <- read.csv(url("https://data.calgary.ca/api/views/35ra-9556/rows.csv?accessType=DOWNLOAD")) 
```

```{r}
df <- x %>% 
  dplyr::mutate(date = START_DT) %>% 
  dplyr::mutate(date = format(as.Date(date, "%Y/%m/%d %I:%M:%S %p"), "%Y")) %>% 
  dplyr::select(date, Count) %>% 
  group_by(date) %>% 
  summarise(count = n())

df
x
```


```{r}
url <- "https://data.calgary.ca/Transportation-Transit/Traffic-Incidents/35ra-9556"

page <- read_html(url)
page
table<- page %>% 
  rvest::html_elements(css = )

table
```

```{r}
library(jsonlite)
library(tidyverse)
url <- "https://data.calgary.ca/resource/35ra-9556.json"
res <- httr::GET(url = url)
# Extracting content
out <- httr::content(x = res, type = "text", encoding = "UTF-8")
# Converting json object to R object
x <- jsonlite::fromJSON(out) 
x


```


```{r}
library(jsonlite)
library(tidyverse)
url <- "https://data.cdc.gov/resource/8pt5-q6wp.json"
res <- httr::GET(url = url)
# Extracting content
out <- httr::content(x = res, type = "text", encoding = "UTF-8")
# Converting json object to R object
x <- jsonlite::fromJSON(out) %>% 
  dplyr::select(indicator, state, time_period_label, value)
x


```



```{r}
library(jsonlite)
library(tidyverse)
url <- "https://crashviewer.nhtsa.dot.gov/CrashAPI/crashes/GetCaseDetails?stateCase=10003&caseYear=2014&state=1&format=json"
res <- httr::GET(url = url)
# Extracting content
out <- httr::content(x = res, type = "text", encoding = "UTF-8")
# Converting json object to R object
x <- jsonlite::fromJSON(out) #%>% 
  #dplyr::select(indicator, state, time_period_label, value)
x


```



```{r}
library(jsonlite)
library(tidyverse)
url <- "https://crashviewer.nhtsa.dot.gov/CrashAPI/analytics/GetInjurySeverityCounts?fromCaseYear=2010&toCaseYear=2021&state=1&format=json"
res <- httr::GET(url = url)
# Extracting content
out <- httr::content(x = res, type = "text", encoding = "UTF-8")
# Converting json object to R object
x <- jsonlite::fromJSON(out) #%>% 
  #dplyr::select(indicator, state, time_period_label, value)
x


```


```{r}
fig.title = "SPY Options - Static"
url = "https://finance.yahoo.com/quote/SPY/options?date=1686873600"
page <- rvest::read_html(url)
calls <- page  %>% rvest::html_table() 
calls
```

